---
title: "MINT demo"
author: "Ellie Sherrard-Smith"
date: "22 March 2021"
output:
  html_document: default
  pdf_document: default
---

Using inputs from 22/03/2021 02:57
Arran/malaria_projects/malaria_cluster_output_to_app/output/save_files

## Single zone data

Here we define the four figures that are shown in the interface (these are already good)

```{r setup, include=FALSE, echo=FALSE}

library(dplyr)
library(plotly)
library(crosstalk)
library(htmltools)
library(DT)

## Set up some mock data with various options selected
# Task - to order the data by strategy cases averted
# then select those within budget

dat1 = readRDS("data/data_aggregate_Vector_tool_updated_params_uncertainty_alter_20201217.RDS")
dim(dat1)
head(dat1)

```



```{r, echo=TRUE}

### Function to pull together a 'region' really easily
region_eg = function(
  index_to_call,##basic data from input ecol set up
  net_use_to_call,irs_to_call,## interventions
  popn,buff,procurement,##set up 
  cost_per_N1,cost_per_N2,costs_S1,
  price_NET_delivery,
  price_IRS_delivery,...){ ## and costs info
  
  ## info from base data
  zone1_ta = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == 0 & 
                      dat1$uncertainty == "mean" & dat1$switch_irs == 0)
  zone1_tb = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == 0 & 
                      dat1$uncertainty == "mean" & dat1$switch_irs == irs_to_call)
  zone1_tc = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == net_use_to_call & 
                      dat1$uncertainty == "mean" & dat1$switch_irs == 0)
  zone1_td = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == net_use_to_call & 
                      dat1$uncertainty == "mean" & dat1$switch_irs == irs_to_call)
  zone1 = rbind(zone1_ta,zone1_tb,zone1_tc,zone1_td)
  
  ## add set up from user inputs
  population_zone1 <- popn
  pro_buffer_zone1 <- (buff + 100) / 100
  procurement <- procurement
  
  ## add cost info
  cost_per_N1 <- cost_per_N1
  cost_per_N2 <- cost_per_N2
  
  price_NET_delivery_zone1 <- price_NET_delivery
  price_IRS_delivery_zone1 <- price_IRS_delivery * population_zone1
  
  costs_N0_zone1    <- 0
  costs_N1_zone1    <- (price_NET_delivery_zone1 + cost_per_N1) * (population_zone1 / procurement * pro_buffer_zone1)
  costs_N2_zone1    <- (price_NET_delivery_zone1 + cost_per_N2) * (population_zone1 / procurement * pro_buffer_zone1)
  costs_S1_zone1    <- 3 * price_IRS_delivery_zone1
  costs_N1_S1_zone1 <- costs_N1_zone1 + costs_S1_zone1
  costs_N2_S1_zone1 <- costs_N2_zone1 + costs_S1_zone1
  
  ## add summary data
  zone1$total_costs = c(costs_N0_zone1,costs_S1_zone1,costs_N1_zone1,costs_N2_zone1,costs_N1_S1_zone1,costs_N2_S1_zone1)
  zone1$total_cases_averted = zone1$cases_averted * population_zone1
  zone1$population_zone1 = population_zone1 
  
  ##lower and upper data
  zone1_ta = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == 0 & 
                      dat1$uncertainty == "low" & dat1$switch_irs == 0)
  zone1_tb = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == 0 & 
                      dat1$uncertainty == "low" & dat1$switch_irs == irs_to_call)
  zone1_tc = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == net_use_to_call & 
                      dat1$uncertainty == "low" & dat1$switch_irs == 0)
  zone1_td = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == net_use_to_call & 
                      dat1$uncertainty == "low" & dat1$switch_irs == irs_to_call)
  zone1low = rbind(zone1_ta,zone1_tb,zone1_tc,zone1_td)
  
  zone1$lower_cases_per_person_3_y = zone1low$cases_per_person_3_years
  
  ##lower and upper data
  zone1_ta = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == 0 & 
                      dat1$uncertainty == "high" & dat1$switch_irs == 0)
  zone1_tb = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == 0 & 
                      dat1$uncertainty == "high" & dat1$switch_irs == irs_to_call)
  zone1_tc = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == net_use_to_call & 
                      dat1$uncertainty == "high" & dat1$switch_irs == 0)
  zone1_td = subset(dat1, dat1$index == index_to_call & dat1$switch_nets == net_use_to_call & 
                      dat1$uncertainty == "high" & dat1$switch_irs == irs_to_call)
  zone1upp = rbind(zone1_ta,zone1_tb,zone1_tc,zone1_td)
  
  zone1$upper_cases_per_person_3_y = zone1upp$cases_per_person_3_years
  
  return(zone1) 
}

zone1 = region_eg(index_to_call = 1184,##any value between 1 and 1206 (check!)
                  net_use_to_call = 0.7,
                  irs_to_call = 0.6,## interventions
                  popn = 140506,
                  buff = 0.07,
                  procurement = 1.8,##set up 
                  cost_per_N1 = 2,
                  cost_per_N2 = 2.75,
                  costs_S1 = 5.73,
                  price_NET_delivery = 2.5,
                  price_IRS_delivery = 5)

zone1$order = c(1,4,2,3,5,6)

zone1 = zone1[order(zone1[, 20]),]

## Efficacy impact tab ##

## Table 1 Impact table
## (the rows in the tool as it stands are good but as an example here)
zone1_Table = data.frame("Interventions" = zone1$intervention,
                         "Net use (%)" = 100*zone1$switch_nets,
                         "IRS cover (%)" = 100*zone1$switch_irs,
                         # "Prevalence under 5 years: Year 1 post intervention" = 
                         round(zone1$prev_1_yr_post,1),
                         # "Prevalence under 5 years: Year 2 post intervention" = 
                         round(zone1$prev_2_yr_post,1),
                         "Prevalence under 5 years: Year 3 post intervention" = 
                           round(zone1$prev_3_yr_post,1),
                         "Relative reduction in prevalence under 5 years (%)" = 
                           round(zone1$reduction_in_prevalence,1),
                         "Mean cases averted per population per year across 3-years since intervention" = 
                           plyr::round_any(zone1$population_zone1 * zone1$cases_per_person_3_years,10))

datatable(zone1_Table,filter = 'none',
          rownames = FALSE,
          caption = "Table.1. Impact table for a single zone",
          style = 'default',extensions = 'Buttons', options = list(
            dom = 'Bfrtip',
            buttons = list('copy', 'print', list(
              extend = 'collection',
              buttons = c('csv', 'excel', 'pdf'),
              text = 'Download'))
          ))

## First figure ##
# output_prev = ## read in appropriate data (need to get this from Arran)
# 
# plot(output_prev[,1],col="grey",pch="",yaxt="n",
#      main = "Projected prevalence in under 5 years",cex.main=1.2,ylim=c(0,1),
#      ylab="Prevalence (%)",xaxt= "n",xlab = "Years of intervention",
#      cex.lab=1.4,cex.axis=1.4,xlim=c(0,50))
# axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,100,20),cex.lab=1.4,cex.axis=1.4)
# axis(1,at=seq(-7,59,12),labels=seq(-1,4,1),cex.lab=1.4,cex.axis=1.4)
# 
# colours = c("grey","blue","aquamarine3","purple","darkred","orange")
# ltys = c(1,1,1,3,2,2)
# lwds = 2
# for(i in 1:6){
#   lines(output_prev[,i],col=colours[i], lty=ltys[i],lwd=2)
# }

## Second figure ##


output_cases_1 = 1000*zone1$cases_per_person_3_years/3
output_cases = output_cases_1[1] - output_cases_1[2:6]

output_cases_2 = 1000*zone1$lower_cases_per_person_3_y/3
output_casesl = output_cases_2[1] - output_cases_2[2:6]

output_cases_3 = 1000*zone1$upper_cases_per_person_3_y/3
output_casesh = output_cases_3[1] - output_cases_3[2:6]

barplot(output_cases, 
        main = "Clinical cases averted per 1000 people per year",
        ylim = c(0,max(output_casesl)),
        ylab = "Cases averted", xlab = "Intervention", xaxt = "n", yaxt = "n",
        col = c("blue","aquamarine3","purple","darkred","orange"))
axis(2,las=2,at=round(seq(0,max(output_cases),length=5),0),
     cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(0.6,5.4,length=5),
     labels = c("pyr-LLIN","PBO ITN","IRS","pyr-LLIN + IRS","PBO ITN + IRS"),
     cex.lab=1.4,cex.axis=1.4)
segments(x0=seq(0.6,5.4,length=5),x1=seq(0.6,5.4,length=5),
         y0=c(output_casesl),
         y1=c(output_casesh))



## Cost effectiveness tab ##

## Table 2 Cost-effectiveness table
## (the rows in the tool as it stands are good but as an example here)
zone1_Table2 = data.frame("Interventions" = zone1$intervention,
                         "Net use (%)" = 100*zone1$switch_nets,
                         "IRS cover (%)" = 100*zone1$switch_irs,
                         "Mean cases averted per 1000 per year across 3-years since intervention" = 
                           plyr::round_any(1000 * zone1$cases_per_person_3_years,10),
                         "Total costs" = plyr::round_any(zone1$total_costs,50),
                         "Costs per case averted across 3-years" = 
                           round(zone1$total_costs /zone1$total_cases_averted,2))

datatable(zone1_Table2,filter = 'none',
          rownames = FALSE,
          caption = "Table.1. Cost effectiveness table for a single zone",
          style = 'default',extensions = 'Buttons', options = list(
            dom = 'Bfrtip',
            buttons = list('copy', 'print', list(
              extend = 'collection',
              buttons = c('csv', 'excel', 'pdf'),
              text = 'Download'))
          ))

## Third figure ##
total_costs = zone1$total_costs
Incremental_efficacy_1 = 1000*zone1$cases_per_person_3_years/3
Incremental_efficacy = Incremental_efficacy_1[1] - Incremental_efficacy_1

Incremental_efficacy_2 = 1000*zone1$lower_cases_per_person_3_y/3
Incremental_efficacyl = Incremental_efficacy_2[1] - Incremental_efficacy_2

Incremental_efficacy_3 = 1000*zone1$upper_cases_per_person_3_y/3
Incremental_efficacyh = Incremental_efficacy_3[1] - Incremental_efficacy_3

plot(total_costs ~ Incremental_efficacy,ylim = c(0,max(total_costs,na.rm = TRUE)),
     main = "Strategy costs over 3 years vs cases averted",
     ylab="Total costs",
     xlab = "cases averted per 1000 people per 3 years",cex.main=1.2,
     col = c("grey","blue","aquamarine3","purple","darkred","orange"),
     pch=19,cex=2,yaxt="n",xlim=c(0,max(Incremental_efficacyl)),cex.lab=1.4,cex.axis=1.4)
axis(2,las=2,at=plyr::round_any(seq(0,max(total_costs),length=5),10),
     cex.lab=1.4,cex.axis=1.4)

col_int = c("grey","blue","aquamarine3","purple","darkred","orange")
for(i in 1:length(Incremental_efficacy)){
  segments(x0=Incremental_efficacyl[i],
           x1=Incremental_efficacyh[i],
           y0=total_costs[i],y1=total_costs[i],col_int[i],lwd=2)
}

output_cases = zone1$total_costs/zone1$cases_averted/zone1$population_zone1

barplot(output_cases[2:6], 
        main = "Strategy costs per case averted",
        ylim = c(0,max(output_cases,na.rm=TRUE)),
        ylab = "Cost per case averted", xlab = "Intervention", xaxt = "n", yaxt = "n",
        col = c("blue","aquamarine3","purple","darkred","orange"))
axis(2,las=2,at=round(seq(0,max(output_cases,na.rm=TRUE),length=5),0),
     cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(0.6,5.4,length=5),
     labels = c("pyr-LLIN","PBO ITN","IRS","pyr-LLIN + IRS","PBO ITN + IRS"),
     cex.lab=1.4,cex.axis=1.4)
# segments(x0=seq(0.6,5.4,length=5),x1=seq(0.6,5.4,length=5),
#          y0=c(output_casesl),
#          y1=c(output_casesh))



```

## Multi zone optimisation

Here, we define the optimisation figures (version 1).
Data are random for 4 zones simply to demostrate the process. 

```{r, include=TRUE}

##################################
##
## Optimisation figures
##
##
##################################

# NOTES - Cases averted per person per per year in each zone
#       - Need to confirm with Arran that I am plotting per year not over 3 years and update this throughout

zone1 = region_eg(index_to_call = 1184,##any value between 1 and 1206 (check!)
                  net_use_to_call = 0.7,
                  irs_to_call = 0.6,## interventions
                  popn = 140506,
                  buff = 0.07,
                  procurement = 1.8,##set up 
                  cost_per_N1 = 2,
                  cost_per_N2 = 2.75,
                  costs_S1 = 5.73,
                  price_NET_delivery = 2.5,
                  price_IRS_delivery = 5)

zone1$order = c(1,4,2,3,5,6)

zone1 = zone1[order(zone1[, 20]),]


zone2 = region_eg(index_to_call = 1084,##any value between 1 and 1206 (check!)
                  net_use_to_call = 0.8,
                  irs_to_call = 0.6,## interventions
                  popn = 213426,
                  buff = 0.07,
                  procurement = 1.8,##set up 
                  cost_per_N1 = 2,
                  cost_per_N2 = 2.75,
                  costs_S1 = 5.73,
                  price_NET_delivery = 1.5,
                  price_IRS_delivery = 5)

zone2$order = c(1,4,2,3,5,6)

zone2 = zone2[order(zone2[, 20]),]


zone3 = region_eg(index_to_call = 184,##any value between 1 and 1206 (check!)
                  net_use_to_call = 0.4,
                  irs_to_call = 0.6,## interventions
                  popn = 14056,
                  buff = 0.07,
                  procurement = 1.8,##set up 
                  cost_per_N1 = 2,
                  cost_per_N2 = 2.25,
                  costs_S1 = 5.73,
                  price_NET_delivery = 2.5,
                  price_IRS_delivery = 5,
                  uncertainty = "mean")

zone3$order = c(1,4,2,3,5,6)

zone3 = zone3[order(zone3[, 20]),]



zone4 = region_eg(index_to_call = 1184,##any value between 1 and 1206 (check!)
                  net_use_to_call = 0.8,
                  irs_to_call = 0.6,## interventions
                  popn = 304567,
                  buff = 0.07,
                  procurement = 1.8,##set up 
                  cost_per_N1 = 2,
                  cost_per_N2 = 2.75,
                  costs_S1 = 5.73,
                  price_NET_delivery = 3,
                  price_IRS_delivery = 8,
                  uncertainty = "mean")

zone4$order = c(1,4,2,3,5,6)

zone4 = zone4[order(zone4[, 20]),]


##############
##
## Add in Dirk Schmacher's optimiser

# Enable this universe
# options(repos = c(
#   ropt = 'https://r-opt.r-universe.dev',
#   CRAN = 'https://cloud.r-project.org'))

# Install some packages
# install.packages('MOI')

# CRAN packages
library(ROI.plugin.glpk)
library(dplyr)

# # install packages from here https://r-opt.r-universe.dev
# library(devtools)
# 
# install_github("r-opt/ROIoptimizer")
# install_github("r-opt/rmpk")

library(ROIoptimzer)
library(rmpk)

# create the input parameters for the model
# hacked together :)
n_zones <- 4
n_interventions <- n_distinct(zone1$intervention)
budget <- sum(mean(zone1$total_costs),
              mean(zone2$total_costs),
              mean(zone3$total_costs),
              mean(zone4$total_costs)) * 0.8 #some random budget

data = rbind(zone1,zone2,zone3,zone4)
data$zone = rep(1:4,each=n_interventions)

cost_df <- distinct(data, zone, intervention, total_costs) %>%
  arrange(intervention, zone) %>%
  group_by(zone) %>% mutate(j = row_number()) %>%
  group_by(intervention) %>% mutate(i = row_number()) %>%
  ungroup()
cases_av_df <- distinct(data, zone, intervention, total_cases_averted) %>%
  arrange(intervention, zone) %>%
  group_by(zone) %>% mutate(j = row_number()) %>%
  group_by(intervention) %>% mutate(i = row_number()) %>%
  ungroup()

cost <- function(zone, intervention) {
  filter(cost_df, i == !!zone, j == !!intervention)$total_costs
}
cases_av <- function(zone, intervention) {
  filter(cases_av_df, i == !!zone, j == !!intervention)$total_cases_averted
}

# small test that it works
# of course this could be a simple matrix instead of a function call (again too lazy)
# cost(1, 1)
# cases_av(1, 1)

# There are different ways to formulate that
# The idea is to have a binary decision variable that models
# if zone i has intervention j. I.e. it is 1 if zone i has intervention j otherwise 0

# create a model with a GLPK as the optimizer
model <- optimization_model(
  ROI_optimizer("glpk", control = list(verbose = TRUE)))

# our decision variable, integer with lower bound 0 and upper bound 1
y <- model$add_variable("y", i = 1:n_zones, j = 1:n_interventions, type = "integer", lb = 0, ub = 1)

# the objective is to maximize cases averted
model$set_objective(sum_expr(y[i, j] * cases_av(i, j), i = 1:n_zones, j = 1:n_interventions), sense = "max")

# subject to a budget constraint
model$add_constraint(sum_expr(y[i, j] * cost(i, j), i = 1:n_zones, j = 1:n_interventions) <= budget)

# Also make sure that each zone gets exactly one intervention
model$add_constraint(sum_expr(y[i, j], j = 1:n_interventions) == 1, i = 1:n_zones)
model$optimize()

res <- model$get_variable_value(y[i, j]) %>%
  filter(value == 1) %>%
  left_join(cost_df) %>%
  left_join(select(cases_av_df, total_cases_averted, i, j), by = c("i", "j"))

# sum(res$total_costs) <= budget
# sum(res$total_costs)
# sum(res$total_cases_averted)

# res
res$cols_int = ifelse(res$intervention == "No intervention","grey",
                      ifelse(res$intervention == "Pyrethroid LLIN only", "blue",
                             ifelse(res$intervention == "Pyrethroid-PBO LLIN only", "aquamarine3",
                                    ifelse(res$intervention == "IRS only", "purple",
                                           ifelse(res$intervention == "Pyrethroid LLIN with IRS",
                                                  "darkred","orange"))))) 
```

This is great, and exactly what we want for the first pass. 

Now I want to see how much we can reduce the budget to acheive at least 90% cases averted relative to this estimate above.
I think we can do this with a logic loop (but do not know exactly how to code this)


```{r, include=TRUE}
n_zones <- 4
n_interventions <- n_distinct(zone1$intervention)
budget <- sum(mean(zone1$total_costs),
              mean(zone2$total_costs),
              mean(zone3$total_costs),
              mean(zone4$total_costs)) * 0.8 #some random budget
budget2 = budget*0.6

data = rbind(zone1,zone2,zone3,zone4)
data$zone = rep(1:4,each=n_interventions)

cost_df <- distinct(data, zone, intervention, total_costs) %>%
  arrange(intervention, zone) %>%
  group_by(zone) %>% mutate(j = row_number()) %>%
  group_by(intervention) %>% mutate(i = row_number()) %>%
  ungroup()
cases_av_df <- distinct(data, zone, intervention, total_cases_averted) %>%
  arrange(intervention, zone) %>%
  group_by(zone) %>% mutate(j = row_number()) %>%
  group_by(intervention) %>% mutate(i = row_number()) %>%
  ungroup()

cost <- function(zone, intervention) {
  filter(cost_df, i == !!zone, j == !!intervention)$total_costs
}
cases_av <- function(zone, intervention) {
  filter(cases_av_df, i == !!zone, j == !!intervention)$total_cases_averted
}

# small test that it works
# of course this could be a simple matrix instead of a function call (again too lazy)
# cost(1, 1)
# cases_av(1, 1)

# There are different ways to formulate that
# The idea is to have a binary decision variable that models
# if zone i has intervention j. I.e. it is 1 if zone i has intervention j otherwise 0

# create a model with a GLPK as the optimizer
model <- optimization_model(
  ROI_optimizer("glpk", control = list(verbose = TRUE)))

# our decision variable, integer with lower bound 0 and upper bound 1
y <- model$add_variable("y", i = 1:n_zones, j = 1:n_interventions, type = "integer", lb = 0, ub = 1)

# the objective is to maximize cases averted
model$set_objective(sum_expr(y[i, j] * cases_av(i, j), i = 1:n_zones, j = 1:n_interventions), sense = "max")

# subject to a budget constraint
model$add_constraint(sum_expr(y[i, j] * cost(i, j), i = 1:n_zones, j = 1:n_interventions) <= budget2)

# Also make sure that each zone gets exactly one intervention
model$add_constraint(sum_expr(y[i, j], j = 1:n_interventions) == 1, i = 1:n_zones)
model$optimize()

res2 <- model$get_variable_value(y[i, j]) %>%
  filter(value == 1) %>%
  left_join(cost_df) %>%
  left_join(select(cases_av_df, total_cases_averted, i, j), by = c("i", "j"))

sum(res2$total_costs) <= budget2
# sum(res2$total_costs)
sum(res2$total_cases_averted) >= 0.9*sum(res$total_cases_averted)

## if TRUE try again until FASLE then step back to the nearest TRUE
## at lower budget estimate (in this example, 59% of the original
## budget is able to be strategised to achieve 90% of the original
## cases averted)


budget <- sum(mean(zone1$total_costs),
              mean(zone2$total_costs),
              mean(zone3$total_costs),
              mean(zone4$total_costs)) * 0.8 #some random budget
budget2 = budget*0.59 ## this is true and 0.58 is false

data = rbind(zone1,zone2,zone3,zone4)
data$zone = rep(1:4,each=n_interventions)

cost_df <- distinct(data, zone, intervention, total_costs) %>%
  arrange(intervention, zone) %>%
  group_by(zone) %>% mutate(j = row_number()) %>%
  group_by(intervention) %>% mutate(i = row_number()) %>%
  ungroup()
cases_av_df <- distinct(data, zone, intervention, total_cases_averted) %>%
  arrange(intervention, zone) %>%
  group_by(zone) %>% mutate(j = row_number()) %>%
  group_by(intervention) %>% mutate(i = row_number()) %>%
  ungroup()

cost <- function(zone, intervention) {
  filter(cost_df, i == !!zone, j == !!intervention)$total_costs
}
cases_av <- function(zone, intervention) {
  filter(cases_av_df, i == !!zone, j == !!intervention)$total_cases_averted
}

# small test that it works
# of course this could be a simple matrix instead of a function call (again too lazy)
# cost(1, 1)
# cases_av(1, 1)

# There are different ways to formulate that
# The idea is to have a binary decision variable that models
# if zone i has intervention j. I.e. it is 1 if zone i has intervention j otherwise 0

# create a model with a GLPK as the optimizer
model <- optimization_model(
  ROI_optimizer("glpk", control = list(verbose = TRUE)))

# our decision variable, integer with lower bound 0 and upper bound 1
y <- model$add_variable("y", i = 1:n_zones, j = 1:n_interventions, type = "integer", lb = 0, ub = 1)

# the objective is to maximize cases averted
model$set_objective(sum_expr(y[i, j] * cases_av(i, j), i = 1:n_zones, j = 1:n_interventions), sense = "max")

# subject to a budget constraint
model$add_constraint(sum_expr(y[i, j] * cost(i, j), i = 1:n_zones, j = 1:n_interventions) <= budget2)

# Also make sure that each zone gets exactly one intervention
model$add_constraint(sum_expr(y[i, j], j = 1:n_interventions) == 1, i = 1:n_zones)
model$optimize()

res2 <- model$get_variable_value(y[i, j]) %>%
  filter(value == 1) %>%
  left_join(cost_df) %>%
  left_join(select(cases_av_df, total_cases_averted, i, j), by = c("i", "j"))

sum(res2$total_costs) <= budget2
# sum(res2$total_costs)
sum(res2$total_cases_averted) >= 0.9*sum(res$total_cases_averted)

res2
```



```{r, include=TRUE}
##########
##
## Add a Table


optimise_table = data.frame(option = c(1,2),
                            "zone 1" = c(res$intervention[res$zone == 1],res2$intervention[res2$zone == 1]),
                            "zone 2" = c(res$intervention[res$zone == 2],res2$intervention[res2$zone == 2]),
                            "zone 3" = c(res$intervention[res$zone == 3],res2$intervention[res2$zone == 3]),
                            "zone 4" = c(res$intervention[res$zone == 4],res2$intervention[res2$zone == 4]),
                            "Total cases averted" = c(plyr::round_any(sum(res$total_cases_averted),20),
                                                      plyr::round_any(sum(res2$total_cases_averted),20)),
                            "Total cost" = c(plyr::round_any(sum(res$total_costs),50),
                                             plyr::round_any(sum(res2$total_costs),50)) )
optimise_table$population = c(sum(data$population_zone1),
                              sum(data$population_zone1))

res_Table_function = function(res){
  
  res_Table = expand.grid("Zone" = res$zone)
  res_Table$"Intervention" = res$intervention
  res_Table$population = ifelse(res_Table$Zone == 1, zone1$population_zone1[1],
                                ifelse(res_Table$Zone == 2, zone2$population_zone1[1],
                                       ifelse(res_Table$Zone == 3, zone3$population_zone1[1],zone4$population_zone1[1])))
  res_Table$"Total cases averted" = plyr::round_any(res$total_cases_averted,20)
  res_Table$"Percentage of cases averted (%)" = 
    round(100*res_Table$"Total cases averted"/sum(res_Table$"Total cases averted"),2)
  res_Table$"Total costs" = plyr::round_any(res$total_costs,50)
  res_Table$"Percentage of total costs (%)" = 
    round(100*plyr::round_any(res$total_costs,50)/sum(plyr::round_any(res$total_costs,50)),2)
  res_Table$"Cost per case averted" = round(res$total_costs/res$total_cases_averted,2)
  res_Table$"Cost per person" = round(res_Table$"Total costs"/res_Table$population,2) 
  res_Table$"cases averted per person" = round(res_Table$"Total cases averted"/res_Table$population,2)
  
  return(res_Table)
}

res_Table = res_Table_function(res)
res_Table2 = res_Table_function(res2)


datatable(optimise_table,
          rownames = FALSE,
          caption = "Table 3. Optimising to minimise cases averted") %>%
  formatStyle(columns = "zone.1", 
              background = styleEqual(c("No intervention",
                                        "Pyrethroid LLIN only",
                                        "Pyrethroid-PBO LLIN only",
                                        "IRS only",
                                        "Pyrethroid LLIN with IRS",
                                        "Pyrethroid-PBO LLIN with IRS"),
                                      c("grey", "blue","lightgreen",
                                        "purple","darkred","orange")))%>%
  formatStyle(columns = "zone.2", 
              background = styleEqual(c("No intervention",
                                        "Pyrethroid LLIN only",
                                        "Pyrethroid-PBO LLIN only",
                                        "IRS only",
                                        "Pyrethroid LLIN with IRS",
                                        "Pyrethroid-PBO LLIN with IRS"),
                                      c("grey", "blue","lightgreen",
                                        "purple","darkred","orange")))%>%
  formatStyle(columns = "zone.3", 
              background = styleEqual(c("No intervention",
                                        "Pyrethroid LLIN only",
                                        "Pyrethroid-PBO LLIN only",
                                        "IRS only",
                                        "Pyrethroid LLIN with IRS",
                                        "Pyrethroid-PBO LLIN with IRS"),
                                      c("grey", "blue","lightgreen",
                                        "purple","darkred","orange")))%>%
  formatStyle(columns = "zone.4", 
              background = styleEqual(c("No intervention",
                                        "Pyrethroid LLIN only",
                                        "Pyrethroid-PBO LLIN only",
                                        "IRS only",
                                        "Pyrethroid LLIN with IRS",
                                        "Pyrethroid-PBO LLIN with IRS"),
                                      c("grey", "blue","lightgreen",
                                        "purple","darkred","orange")))


##
## For this table - ideally we want to have the cheapest option within 10%
## of the best option as row 2
## We want to be able to click on a row and produce the next 2 figures and table
## for each row
##
##
res = res[order(res$zone),]
res2 = res2[order(res2$zone),]

barplot(res_Table$"Total cases averted" ~ res_Table$Zone,
        col=res$cols_int,
        main = paste("Total budget constraint USD:",plyr::round_any(budget,100)),
        ylim = c(0,max(res$total_cases_averted)+0.25*max(res$total_cases_averted)),
        ylab = "Total cases averted",
        xlab = "Zone")


legend("topright",
       legend = c("No intervention",
                  "Pyrethroid LLIN only",
                  "Pyrethroid-PBO ITN only",
                  "IRS only",
                  "Pyrethroid LLIN with IRS",
                  "Pyrethroid-PBO ITN with IRS"),
       ncol = 2, col=c("grey", "blue","lightgreen",
                       "purple","darkred","orange"),pch=15)


barplot(res_Table$"cases averted per person" ~ res_Table$Zone,
        col=res$cols_int,
        main = paste("Total budget constraint USD:",plyr::round_any(budget,100)),
        yaxt = "n",
        ylab = "Cases averted per person",
        xlab = "Zone")
axis(2,las=2,round(seq(0,max(res_Table$"cases averted per person"),length=5),2))


legend("topright",
       legend = c("No intervention",
                  "Pyrethroid LLIN only",
                  "Pyrethroid-PBO ITN only",
                  "IRS only",
                  "Pyrethroid LLIN with IRS",
                  "Pyrethroid-PBO ITN with IRS"),
       ncol = 2, col=c("grey", "blue","lightgreen",
                       "purple","darkred","orange"),pch=15)


## And the data for the chosen optimisation 'row' from optimise_table
res_Table[5,] = c("TOTAL","",
                  colSums(res_Table[,3:4]),
                  round(sum(as.numeric(res_Table[,5]))),
                  sum(as.numeric(res_Table[,6])),
                  round(sum(as.numeric(res_Table[,7]))),"","","")


datatable(res_Table,
          rownames = FALSE,
          caption = "Table 3. Optimising to minimise cases averted")


## or if the user selects the alternative option

res_Table2[5,] = c("TOTAL","",
                  colSums(res_Table2[,3:4]),
                  round(sum(as.numeric(res_Table2[,5]))),
                  sum(as.numeric(res_Table2[,6])),
                  round(sum(as.numeric(res_Table2[,7]))),"","","")


datatable(res_Table2,
          rownames = FALSE,
          caption = "Table 3. Optimising to minimise cases averted within 10% best-case for reduced budget")



```



